Distributed Environment for Auctioning Virtual Power System Resources

### 2022-02-04 other/paper-aicts-chekan.tex
Elimination of overfill box
Proof read of Introduction

The powerstand game session consists of stages. One of the stages is auctions for the ownership of objects of the conditional microdistrict assembled by the participants of the power grid. The grid is subsequently simulated, accounting parameters of energy efficiency and profitability. Since the set of objects directly impacts the simulation result, it is crucial to carry out reliably and promptly this stage of work with the stand. The problem is the imperfection of the manual auction version when the hosts independently collect the participants' bids using material (paper) or digital media (messages in a messenger application). We proposed automating this stage and introducing it into the existing software packages to improve reliability. Power system modeling is an already essentially automated process. Reducing external dependencies through additional automation will increase the integrity of the software and hardware complex and increase the dynamics of the activities, as well as reduce the requirements for operator qualification requirements, which is especially important when deploying the stand as an educational tool at various sites where the direct presence of administrators is not expected.

The first iteration was successfully developed and implemented as a powerstand module [4]. However, as the popularity of virtual formats of educational and competitive events grows, it becomes necessary to implement a new version of the module for supporting the distributed environment of virtual auctions when participants work at stands located in different geographically distant points. The result of designing and implementing such an environment is presented in the research.

@@

Building a network architecture with the expectation of implementation in consumer products involves following the standards for building computer networks that have been formed over the past half-century, including the OSI model and the protocol group of the transport and session layers of this model [8]. These standards have been tested by time and practice, so the task of developing and designing new solutions belongs to the application and session levels, while solutions at the session level and below are most often the de facto standard, and working with them comes down to choosing options.

@@

Jia and Zhou also mention replication to provide fault tolerance [5, p. 240]. In addition, replication solves two more problems - increasing the availability of the service (if one node fails, the functionality supports the other) and improving performance (reducing response time by dividing the data flow across different servers). Although these provisions are described mainly for decentralized systems, replication in a centralized architecture (if we consider working with data separately) also allows them to be achieved.

Software solutions for implementing distributed architectures are often reduced to embedded libraries for network interaction and message passing. It is worth highlighting libraries for implementing remote procedure call (RPC), particularly gRPC [9], a full-fledged cross-platform solution for distributed computing. However, the most common solutions related to remote message passing (message passing) require the connection of additional libraries that carry additional dependencies. It makes sense to write code for network functionality optimized for specific conditions and requirements depending on the task.

@@

   \bibitem{b22} Comparison of JSON Like Serializations. URL:\url{http://zderadicka.eu/comparison-of-json-like-serializations-json-vs-ubjson-vs-messagepack-vs-cbor/} (access date: 21.05.2021)

>>>>

The powerstand game session consists of stages. One of the stages is auctions for the ownership of objects of a playing ground district assembled by the participants of the power grid. The grid is subsequently simulated, accounting parameters of energy efficiency and profitability. Since the set of objects directly impacts the simulation result, it is crucial to carry out reliably and promptly this stage of work with the stand. The problem is the imperfection of the manual auction version when the hosts independently collect the participants' bids using material (paper) or digital media (messages in a messenger application). We proposed automating this stage and introducing it into the existing software packages to improve reliability. Power system modeling is an already essentially automated process. Reducing external dependencies through additional automation will increase the integrity of the software and hardware complex and increase the dynamics of the activities, as well as reduce the requirements for operator qualification requirements, which is especially important when deploying the stand as an educational tool at various sites where the direct presence of administrators is not expected.

The first version of software was successfully developed and implemented as a powerstand module~[4]. However, as the popularity of virtual formats of educational and competitive events grows, it becomes necessary to implement an extension of the module for supporting the distributed environment of virtual auctions when participants work at stands located in different geographically distant points. The result of designing and implementing such an environment is presented in the research.

@@

Building a network architecture with the expectation of implementation in consumer products involves following the standards for building computer networks that have been formed over the past half-century, including the OSI model and the protocol group of the transport and session layers of this model [8]. These standards have been tested by time and practice, so the task of developing and designing new solutions belongs to the application and session levels, while solutions at the session level and below are most often the \emph{de facto} standard, and working with them comes down to choosing options.

@@

Jia and Zhou also mention replication to provide fault tolerance [5, p. 240]. In addition, replication solves two more problems - increasing the availability of the service (if one node fails, the functionality supports the other) and improving performance (reducing response time by distributing the data flow across different servers). Although these provisions are described mainly for decentralized systems, replication in a centralized architecture (if we consider working with data separately) also allows them to be achieved.

Software solutions for implementing distributed architectures are often reduced to embedded libraries for network interaction and message passing. It is worth highlighting libraries for implementing remote procedure call (RPC), particularly gRPC [9], a full-fledged cross-platform solution for distributed computing. However, the most common solutions related to remote message passing require utilization of other libraries that pull additional dependencies. It makes sense to write code for network functionality optimized for specific conditions and requirements depending on the task.

@@

   \bibitem{b22} Comparison of JSON Like Serializations. URL:\texttt{http://zderadicka.eu/comparison-of-json-like-serializations-json-vs-ubjson-vs-messagepack-vs-cbor/} (access date: 21.05.2021)
